\input{title.tex}

### 2022-05-04 docs/papers/01_manuscript/03_results.tex
feat(new-plot-fig-3): re-draw fig 3
BREAKING CHANGE:
fix(fix-bad-unicode-in-bodin2017b-and-compile.): compiling by vscode
feat(results,-fig3,-compile-manuscript): add figure 3 in the main text
BREAKING CHANGE:

%\subsection{INSTITUTIONAL SHIFTS IMPACT ON WATER USE OF THE YRB}
\subsection{Institutional shifts impact on water use of the YRB}
\label{result-2}
% 结果一：展示制度转变带来的用水量变化

\label{result-1-p2}
Our estimation of theoretical water use suggests that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without an institutional shift (Figure~\ref{main_results}A).
From 1988 to 1998 on average, while the estimation of annual water use only suggests $956.38$ billion $m^3$, the observed water use of the YRB provinces reached $1038.36$ billion $m^3$ in sum, $8.57\%$ increased.
However, after the institution shifted again in 1998 (98-UBR), the trend of increasing water use appeared to be effectively suppressed. From 1998 to 2008, the total observed water use decreased by $4.9$ billion $m^3/yr$ per year, while the estimation of water use still suggests $10.3$ billion $m^3/yr$ increases (Figure~\ref{main_results} B).
The increased water uses after 87-WAS aligns with the fact that badly drying-up of the surface streamflow from 1987 to 1998, which was an obvious touchstone of river degradation and environmental crisis (Figure~\ref{main_results}C).
On the other hand, the 98-UBR ended river depletion, despite the density of droughts still increasing for decades (from $0.47$ after 87-WAS to $0.62$ after 98-UBR on average) (Figure~\ref{main_results}C).

@@

%\subsection{REGIONAL DIFFERENCES IN RESPONSES TO INSTITUTIONAL SHIFTS}
\subsection{Regional differences in responses to institutional shifts}
\label{result-3}
% 结果2部分：展示区域相应差异
Our results also suggest huge differences between patterns of provinces in their responses to the two institutional shifts.
During the decade after the 87-WAS, the proportion of accelerated water use for each province (the proportion of actual water use exceeding the predicted water use by the model) has a significant correlation ($p<0.05$) to the Yellow River water use (Figure~\ref{upset}A).
While non-obvious impacts (less than $10\%$ in proportion) for most provinces, the apparent acceleration was prominent for the central water-using provinces (e.g., Inner Mongolia, Henan, and Shandong. Figure~\ref{upset}B).
In particular, Inner Mongolia and Shandong, both provinces that exceeded the prescribed water uses of the 87-WAS, used $44.25\%$ and $25.69\%$ more water uses than the prediction from 1987 to 1998, respectively.
In addition, the deficits of the water quota for each province (expressed by the difference between the water quota in 87-WAS and an expectation in water demands from a beforehand plan) have no significant ($p>0.05$) correlation to the acceleration.
By contrast, after the 98-UBR, except Shanxi (whose water quota has always been abundant since the 87-WAS) had an evident ($17.53\%$) increase in water use, almost all provinces have seen evident declines in water use ($-12.5\%$ on average).
Furthermore, neither the Yellow River water use nor the deficits correlate with the decreased proportions.

\begin{figure*}[!h]
    \centering
    \includegraphics[width=32pc]{outputs/combined_upset.pdf}
    \caption{Responses of the provinces to the institutional shifts (upper: the 87-WAS, lower: the 98-UBR).
        \textbf{A.} The partial correlation coefficient between water use (WU) of Yellow River (YR), unsatisfied ratio (compared with requirements in water plan and supply in the 87-WAS), and the average accelerated ratio.
        \textbf{B.} Average accelerated ratio of water uses for each province in the YRB during the decade after 87-WAS (from 1987 to 1998).
        \textbf{Mian users:} Major water consumption provinces (over the median).
        \textbf{Overused:} violate the 87-WAS in average water uses.
    }
    \label{upset}
\end{figure*}

>>>>

%\subsection{INSTITUTIONAL SHIFTS IMPACT ON WATER USE OF THE YRB}
\subsection{Institutional shifts impact on water use}
\label{result-2}
% 结果一：展示制度转变带来的用水量变化

\label{result-1-p2}
Our estimation of theoretical water use suggests that the institutional shift in 1987 (87-WAS) stimulated the provinces to withdraw more water than would have been used without an institutional shift (Figure~\ref{main_results}A).
From 1988 to 1998, on average, while the estimation of annual water use only suggests $956.38$ billion $m^3$, the observed water use of the YRB provinces reached $1038.36$ billion $m^3$ in sum, $8.57\%$ increased.
However, after the institution shifted again in 1998 (98-UBR), the trend of increasing water use appeared to be effectively suppressed. From 1998 to 2008, the total observed water use decreased by $4.9$ billion $m^3/yr$ per year, while the estimation of water use still suggests $10.3$ billion $m^3/yr$ increases (Figure~\ref{main_results} B).
The increased water uses after 87-WAS aligns with the fact that badly drying-up of the surface streamflow from 1987 to 1998, which was an obvious touchstone of river degradation and environmental crisis (Figure~\ref{main_results}C).
On the other hand, the 98-UBR ended river depletion, despite the density of droughts still increasing for decades (from $0.47$ after 87-WAS to $0.62$ after 98-UBR on average) (Figure~\ref{main_results}C).

@@

%\subsection{REGIONAL DIFFERENCES IN RESPONSES TO INSTITUTIONAL SHIFTS}
\subsection{Institutional effects on regulating differences}
\label{result-3}
% 结果2部分：展示区域相应差异
Our results also suggest differences between patterns of provinces in their responses to the two institutional regulating.
During the decade after the 87-WAS, the major water-using provinces (e.g., Inner Mongolia, Henan, Shandong) had apparent accelerations (Figure~\ref{regulating}).
The proportion of increased (or decreased) water use for each province (over the estimated water use by the model) has a significant correlation (partial correlation coefficient is $0.84$, $p<0.05$) to the actual water use from the Yellow River.
In particular, Inner Mongolia and Shandong, both provinces that exceeded the prescribed water uses of the 87-WAS, used $44.25\%$ and $25.69\%$ more water uses than the prediction from 1987 to 1998, respectively.
By contrast, after the 98-UBR, except Shanxi (whose water quota has always been far abundant over its actual water use since the 87-WAS) had an evident ($17.53\%$) increase in water use, almost all provinces have seen evident declines in water use ($-12.5\%$ on average).
Furthermore, the regulated water use of provinces was not correlated ($-0.03$) with their water use from the Yellow River in proportions.

\begin{figure*}[!h]
    \centering
    \includegraphics[width=32pc]{outputs/fig3.pdf}
    \caption{
        Regulating differences for provinces in the YRB.
        Red and green bars denote actual water use over the estimation from the model in a decade after the institutional shift -the 87-WAS and the 98-UBR, respectively.
        The grey bars indicate the proportions of actual water use for each province to total water use of the provinces in a decade after the institutional shift.
        The triangles mark the water quotas assigned in the institution, scaled into ratios by the same total actual water use, too.
    }
    \label{regulating}
\end{figure*}
